Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex
Unbackwards the text

\begin{figure*}[tb]
    \centering
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{In the first two plots, the cumulative number of instances solved over time, for the
        induced and non-induced problems, with different values of $k$. We also show the results of
        iteratively decreasing $k$ until a solution is found, and in the induced case, the
        performance of two leading maximum common subgraph algorithms. In the third plot, results
        comparing our algorithm with iteratively decreasing $k$ to other approaches on maximum
        common induced subgraph instances.}\label{figure:runtimes}
\end{figure*}

@@

\begin{proof}[Proof of \cref{prop:paths}]
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$, $P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the end vertex on the
\begin{align*}
 \\
 = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\
 = & \{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} .
\end{align*}
So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.

>>>>

\begin{figure*}[tb]
    \centering
    \includegraphics*{gen-graph-runtimes.pdf}
    \caption{In the first two plots, the cumulative number of instances solved over time, for the
        induced and non-induced problems, with different values of $k$. We also show the results of
        iteratively increasing $k$ until a solution is found, and in the induced case, the
        performance of two leading maximum common subgraph algorithms. In the third plot, results
        comparing our algorithm with iteratively increasing $k$ to other approaches on maximum
        common induced subgraph instances.}\label{figure:runtimes}
\end{figure*}

@@

\begin{proof}[Proof of \cref{prop:paths}]
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
$P_{2} = \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \}$. As we are looking at paths of length 2, the
intermediate vertices lie in both neigbour vertex sets of $p$ and $q$. We can rewrite $P_{2}$ as
$P_{2} = \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \}$, in other words the intermediate vertices lie in the intersection of the neighbour sets of $p$ and $q$,
$P_{2}=\{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \}$. So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq \deg(p)$.
